\section{Literature}

This section positions the project relative to four literatures: input-market buyer power, production networks and misallocation, China's vertical structure, and firm position in global production lines.

\subsection{Input-Demand Wedges and Buyer-Side Frictions}

The starting point of the paper is an intermediate input-demand wedge. This object is not interpreted mechanically as a pure markdown. Instead, the paper first measures the wedge and then asks whether it behaves like a buyer-side friction by relating it to downstream concentration, buyer size, supplier fragmentation, accounts payable, accounts receivable, and payment pressure.

\subsection{Production Networks and Policy Targeting}

The paper follows the production-network logic that local distortions can matter for other sectors through input-output linkages. The distinctive step in this project is to map downstream buyer-side wedges into upstream exposure using sales-destination weights from the upstream industry's perspective. This separates the paper from a simple industry-level wedge exercise and turns it into a test of network-transmitted upstream stress and policy response.

\subsection{China's Vertical Structure and Upstream SOE Mechanisms}

The China vertical-structure literature is a core background and a competing explanation. Li, Liu, Lu and Wang document a structure in which upstream industries are dominated by SOEs while downstream industries are more privately competitive. Their mechanism is upstream SOE monopoly and credit subsidies as a possible second-best response to upstream under-supply. This paper borrows the vertical-structure background and the second-best policy logic, but studies a different friction: downstream input-demand wedges and payment-related buyer-side distortions.

The domestic upstream-SOE literature also provides an important comparison. Liu, Wang and Zhan study how upstream SOE presence affects downstream private-firm productivity. That direction is the opposite of this paper. Their contribution is useful for the empirical design because it shows how to combine firm data with input-output tables and because it identifies controls and alternative mechanisms, including upstream SOE share, upstream SOE concentration, SOE policy support, local financial crowding-out, and central-versus-local SOE heterogeneity.

\subsection{Upstreamness, GVC Position, and Competing Mechanisms}

Firm position in production lines is another relevant source of variation. Chor, Manova and Yu show that Chinese firms' import upstreamness, export position, and production-stage span vary with productivity, size, experience, and foreign demand. This literature is useful for constructing and interpreting upstreamness and production-chain exposure measures. It also creates a robustness requirement: the paper must show that the estimated upstream exposure effect is not simply capturing GVC upgrading, firm lifecycle dynamics, processing trade, export demand shocks, or generic movement along the production line.
